# Load libraries
library(airGR)
library(tidyverse)
library(hydroGOF)
library(patchwork)
library(glue)
library(randomForest)
library(pls)

# DataAltiExtrapolation_NPL: Create a custom function by changing some values of original function 

```{r}
DataAltiExtrapolation_NPL <- function (DatesR, Precip, PrecipScale = TRUE, TempMean, TempMin = NULL, 
  TempMax = NULL, ZInputs, HypsoData, NLayers,GradT=lr, verbose = TRUE) 
{
  GradP_Valery2010 <- 0
  HypsoData <- as.double(HypsoData)
  ZInputs <- as.double(ZInputs)
  ZLayers <- as.double(rep(NA, NLayers))
  if (!identical(HypsoData, as.double(rep(NA, 101)))) {
    nmoy <- 100%/%NLayers
    nreste <- 100%%NLayers
    ncont <- 0
    for (iLayer in 1:NLayers) {
      if (nreste > 0) {
        nn <- nmoy + 1
        nreste <- nreste - 1
      }
      else {
        nn <- nmoy
      }
      if (nn == 1) {
        ZLayers[iLayer] <- HypsoData[ncont + 1]
      }
      if (nn == 2) {
        ZLayers[iLayer] <- 0.5 * (HypsoData[ncont + 
          1] + HypsoData[ncont + 2])
      }
      if (nn > 2) {
        ZLayers[iLayer] <- HypsoData[ncont + nn/2 + 
          1]
      }
      ncont <- ncont + nn
    }
  }
  if (identical(ZInputs, HypsoData[51]) & NLayers == 1) {
    LayerPrecip <- list(as.double(Precip))
  }
  else {
    GradP <- GradP_Valery2010
    TabGradP <- rep(GradP, length(Precip))
    Zthreshold <- 4000
    LayerPrecip_mat <- sapply(1:NLayers, function(iLayer) {
      if (ZLayers[iLayer] <= Zthreshold) {
        prcp <- as.double(Precip * exp(TabGradP * (ZLayers[iLayer] - 
          ZInputs)))
      }
      else {
        if (ZInputs <= Zthreshold) {
          prcp <- as.double(Precip * exp(TabGradP * 
            (Zthreshold - ZInputs)))
        }
        else {
          prcp <- as.double(Precip)
        }
      }
      return(prcp)
    })
    if (PrecipScale) {
      LayerPrecip_mat <- LayerPrecip_mat/rowMeans(LayerPrecip_mat) * 
        Precip
      LayerPrecip_mat[is.nan(LayerPrecip_mat)] <- 0
    }
    LayerPrecip <- as.list(as.data.frame(LayerPrecip_mat))
  }
  LayerTempMean <- list()
  LayerTempMin <- list()
  LayerTempMax <- list()
  if (identical(ZInputs, HypsoData[51]) & NLayers == 1) {
    LayerTempMean[[1]] <- as.double(TempMean)
    if (!is.null(TempMin) & !is.null(TempMax)) {
      LayerTempMin[[1]] <- as.double(TempMin)
      LayerTempMax[[1]] <- as.double(TempMax)
    }
  }
  else {
    #GradT <- GradT
    for (iLayer in 1:NLayers) {
      LayerTempMean[[iLayer]] <- as.double(TempMean + 
        (ZInputs - ZLayers[iLayer]) * GradT)
      if (!is.null(TempMin) & !is.null(TempMax)) {
        LayerTempMin[[iLayer]] <- as.double(TempMin + 
          (ZInputs - ZLayers[iLayer]) * GradT)
        LayerTempMax[[iLayer]] <- as.double(TempMax + 
          (ZInputs - ZLayers[iLayer]) * GradT)
      }
    }
  }
  LayerFracSolidPrecip <- list()
  Zthreshold <- 1500
  Option <- "USACE"
  if (!is.na(ZInputs)) {
    if (ZInputs < Zthreshold & !is.null(TempMin) & !is.null(TempMax)) {
      Option <- "Hydrotel"
    }
  }
  for (iLayer in 1:NLayers) {
    if (Option == "Hydrotel") {
      TempMin <- LayerTempMin[[iLayer]]
      TempMax <- LayerTempMax[[iLayer]]
      SolidFraction <- 1 - TempMax/(TempMax - TempMin)
      SolidFraction[TempMin >= 0] <- 0
      SolidFraction[TempMax <= 0] <- 1
    }
    if (Option == "USACE") {
      USACE_Tmin <- -1
      USACE_Tmax <- 3
      TempMean <- LayerTempMean[[iLayer]]
      SolidFraction <- 1 - (TempMean - USACE_Tmin)/(USACE_Tmax - 
        USACE_Tmin)
      SolidFraction[TempMean > USACE_Tmax] <- 0
      SolidFraction[TempMean < USACE_Tmin] <- 1
    }
    LayerFracSolidPrecip[[iLayer]] <- as.double(SolidFraction)
  }
  namesLayer <- sprintf("L%i", seq_along(LayerPrecip))
  names(LayerPrecip) <- namesLayer
  names(LayerTempMean) <- namesLayer
  if (!is.null(TempMin) & !is.null(TempMax)) {
    names(LayerTempMin) <- namesLayer
    names(LayerTempMax) <- namesLayer
  }
  names(LayerFracSolidPrecip) <- namesLayer
  return(list(LayerPrecip = LayerPrecip, LayerTempMean = LayerTempMean, 
    LayerTempMin = LayerTempMin, LayerTempMax = LayerTempMax, 
    LayerFracSolidPrecip = LayerFracSolidPrecip, ZLayers = ZLayers))
}
```

# Next, assign the custom function to the package and assign original function to custom function.
# The call to environment() assures that the function will be able to call other hidden functions from the package.

# The call to assignInNamespace() assures that other functions from the package will call your updated version of the function.
# See: https://stackoverflow.com/questions/24331690/modify-package-function

```{r}
environment(DataAltiExtrapolation_NPL)<- asNamespace('airGR')
assignInNamespace("DataAltiExtrapolation_Valery", DataAltiExtrapolation_NPL, ns = "airGR")
```
# DERIVE HYPSOMETRY
```{r}
hypso_df <- read_csv(glue::glue("E:/Project/GR4JCN/hypso/{stn}.csv"))

ggplot(hypso_df)+
  geom_line(aes(Elevation,Area))
hypso <- data.frame()
for (i in 1:99){
  hypso <- hypso %>% bind_rows(hypso_df %>% filter(abs(Area-i)==min(abs(Area-i))))}

le <- 320
he <- 3613
hypso <- c(le,hypso$Elevation,he) 
```

# Add Temperature Data to BasinObs

```{r}
lr <- 0.0052 #Lapse-rate
df_fill <- read_csv("E:/Project/BasinData/Inputs/temp_filled.csv")

basin_temp <- df_fill %>% filter(stn==1206) %>% rowwise() %>% mutate(Tmean=mean(c(Tmax,Tmin),na.rm=T)) %>% filter(year(Date) %in% c(2000:2015))

BasinObs$Tmean <- temp$Tavg

ZInputs = 684
BasinObs <- BasinObs %>% mutate(Tmed=Tmean+(median(hypso)-ZInputs)*(-lr))

Lat = 28.27
BasinObs <- BasinObs %>% mutate(Emed = PE_Oudin(as.POSIXlt(DatesR)$yday+1,
                                 Temp=Tmed,
                                 Lat=Lat,
                                 LatUnit="deg"))
```

## preparation of the InputsModel object

```{r}
Input <- CreateInputsModel(FUN_MOD = RunModel_CemaNeigeGR4J,
                                 DatesR = as.POSIXlt(BasinObs$DatesR), Precip = BasinObs$P,
                                , PotEvap = BasinObs$Emed, TempMean = BasinObs$Tmean,
                                 ZInputs = ZInputs,
                                 HypsoData = hypso, NLayers = 5)
```

## ---- calibration step

```{r}
## calibration period selection
warmup_period <- seq(which(format(BasinObs$DatesR, format = "%Y-%m-%d") == "2000-01-01"),which(format(BasinObs$DatesR, format = "%Y-%m-%d") == "2000-12-31"))

calib_period <- seq(which(format(BasinObs$DatesR, format = "%Y-%m-%d") == "2001-01-01"),which(format(BasinObs$DatesR, format = "%Y-%m-%d") == "2006-12-31"))

valid_period <- seq(which(format(BasinObs$DatesR, format = "%Y-%m-%d") == "2007-01-01"),which(format(BasinObs$DatesR, format = "%Y-%m-%d") == "2010-12-31"))

Run_calib <- CreateRunOptions(FUN_MOD = RunModel_CemaNeigeGR4J,InputsModel = Input, IndPeriod_Run = calib_period,IndPeriod_WarmUp = warmup_period)

Run_valid <- CreateRunOptions(FUN_MOD = RunModel_CemaNeigeGR4J,InputsModel = Input, IndPeriod_Run = valid_period)
```

```{r}
Crit_cal <- CreateInputsCrit(FUN_CRIT = ErrorCrit_NSE,InputsModel = Input, RunOptions = Run_calib, Obs = BasinObs$Qmm[calib_period])

Crit_val <- CreateInputsCrit(FUN_CRIT = ErrorCrit_NSE,InputsModel = Input, RunOptions = Run_valid, Obs = BasinObs$Qmm[valid_period])
```

```{r}
# Define Calibration algorithm and calibrate
glomean <- data.frame()
for (stn in stns){
  load(glue("E:/Project/GR4JCN/BasinObs/{stn}.Rda"))
  Input <- CreateInputsModel(FUN_MOD = RunModel_CemaNeigeGR4J,
                                 DatesR = as.POSIXlt(BasinObs$DatesR), Precip = BasinObs$P,
                                , PotEvap = BasinObs$Emed, TempMean = BasinObs$Tmean,
                                 ZInputs = ZInputs,
                                 HypsoData = hypso, NLayers = 5)

Run_calib <- CreateRunOptions(FUN_MOD = RunModel_CemaNeigeGR4J,InputsModel = Input, IndPeriod_Run = calib_period,IndPeriod_WarmUp = warmup_period)

Run_valid <- CreateRunOptions(FUN_MOD = RunModel_CemaNeigeGR4J,InputsModel = Input, IndPeriod_Run = valid_period)


Crit_cal <- CreateInputsCrit(FUN_CRIT = ErrorCrit_NSE,InputsModel = Input, RunOptions = Run_calib, Obs = BasinObs$Qmm[calib_period])

Crit_val <- CreateInputsCrit(FUN_CRIT = ErrorCrit_NSE,InputsModel = Input, RunOptions = Run_valid, Obs = BasinObs$Qmm[valid_period])

params = params_glom

sim_calib <- RunModel_CemaNeigeGR4J(InputsModel=Input,RunOptions=Run_calib,Param = params)

sim_valid <- RunModel_CemaNeigeGR4J(InputsModel = Input, RunOptions = Run_valid, Param = params)

calib_NSE <- ErrorCrit_NSE(InputsCrit = Crit_cal,OutputsModel = sim_calib)$CritValue

valid_NSE <- ErrorCrit_NSE(InputsCrit = Crit_val,OutputsModel = sim_valid)$CritValue

glomean <- glomean %>% bind_rows(data.frame(stn=stn,cal=calib_NSE,val=valid_NSE,params=I(list(as.vector(params)))))
}
```

```{r}
# Run model in calibration and validation periods
results <- data.frame()
for (stn in stns){
  load(glue("E:/Project/GR4JCN/BasinObs/{stn}.Rda"))
  Input <- CreateInputsModel(FUN_MOD = RunModel_CemaNeigeGR4J,
                                 DatesR = as.POSIXlt(BasinObs$DatesR), Precip = BasinObs$P,
                                , PotEvap = BasinObs$Emed, TempMean = BasinObs$Tmean,
                                 ZInputs = ZInputs,
                                 HypsoData = hypso, NLayers = 5)
  Run_calib <- CreateRunOptions(FUN_MOD = RunModel_CemaNeigeGR4J,InputsModel = Input, IndPeriod_Run = calib_period,IndPeriod_WarmUp = warmup_period)

  Run_valid <- CreateRunOptions(FUN_MOD = RunModel_CemaNeigeGR4J,InputsModel = Input, IndPeriod_Run = valid_period)
  
  Crit_cal <- CreateInputsCrit(FUN_CRIT = ErrorCrit_NSE,InputsModel = Input, RunOptions = Run_calib, Obs = BasinObs$Qmm[calib_period])

  Crit_val <- CreateInputsCrit(FUN_CRIT = ErrorCrit_NSE,InputsModel = Input, RunOptions = Run_valid, Obs = BasinObs$Qmm[valid_period])
  
  params= (test_PS %>% filter(st.id==115))$params[[1]] 

  sim_calib <- RunModel_CemaNeigeGR4J(InputsModel=Input,RunOptions=Run_calib,Param = params)

  sim_valid <- RunModel_CemaNeigeGR4J(InputsModel = Input, RunOptions = Run_valid, Param = params)

  calib_NSE <- ErrorCrit_NSE(InputsCrit = Crit_cal,OutputsModel = sim_calib)$CritValue
  
  valid_NSE <- ErrorCrit_NSE(InputsCrit = Crit_val,OutputsModel = sim_valid)$CritValue
  
  results <- results %>% bind_rows(data.frame(stn=stn,cal=calib_NSE,val=valid_NSE))
}
```


